\documentclass{article}
% \usepackage[document]{ragged2e}
\usepackage{blindtext}
\usepackage{hyperref}
\usepackage{booktabs}
\hypersetup{colorlinks,linkcolor=black}
\title{Information Gathering Assignment}
\author{Ahmed Ashraf Mohamed\\2103134 \and Shahd Ahmed Taher\\20201447207}
\date{}
\begin{document}
\maketitle
\tableofcontents
\section{Interview Questions}
\subsection{Types of Questions}
We are going to use all the types of interview Questions
\begin{enumerate}
    \item Funnel Type
    \item Pyramid Type
    \item Diamond Type
\end{enumerate}
\subsection{Funnel type questions}
The funnel type questions are going to be used for the first interview with the users as it gives the user the freedom to express their opinions about the proposed system and then expand by close-ended questions which shall gives more
information about our requirements.

Users:
\begin{enumerate}
    \item What do you expect the system to output in the generated reports?
    \item How do you think the system will help you to solve current managerial problems?
    \item To what degree would you assess the sensitivity of the data used?
    \item What additional features would you like to see in the system?
    \item Should the interface contain a dashboard of the most important data?
\end{enumerate}
\subsection{Pyramid type questions}
The Pyramid type questions are going to be suitable for an admin interview as we need identify intended usage of the systems by the admin, and the interview expands by asking questions about  expected usage of the system.

Admin:
\begin{enumerate}
    \item Should the system include a data management subsystem?
    \item Should the system include a review capability of the reports produced before being finalized?
    \item What is your main concern about the analysis of data in the system?
    \item What are the possible issues that you might face during the administration of the system?
    \item What are your thoughts about the interface that is going to be used in the data management subsystem?
\end{enumerate}
\subsection{Diamond type questions}
The diamond type questions are going to used for the third and last interview with the head of Finance department. This Type shall gives more information about the head of Finance department expectations of the contents of the system as well as any performance metrics not thought about beforehand.

Head of Finance department
\begin{enumerate}
    \item Should the reports produced by the system include projection of revenue gain and possible losses?
    \item What finical performance metrics do you expect to be included in produced reports?
    \item Do you think the systems might help with identifying finical trends?
    \item How often should the finical reports be produced or updated in the system?
    \item Should the ability to display different currencies and conversion capability?
\end{enumerate}

\section{Structure of the interview}
\textbf{The Interview is going to be semi-Structured to allow follow-up questions that elaborate more on the answers.}

\section{Report of The Simulated Interviews}
\subsection{The First interview (Users)}
\subsubsection{Interviewee}
\textbf{Users: Mid to Higher management}
\subsubsection{Interviewer}
\textbf{Shahd Ahmed}
\subsubsection{Purpose of the Interview}
The purpose of it is the collection more information about the requirements of the interface subsystem as well as the reporting subsystem in the aspects of clarity and simplicity.
\subsubsection{Summary}
After asking the main five question, we found that since the sensitivity of data is not extremely high a cloud computing solution is going to be used, as well as the inclusion filtering capability of the data to able to exploratory analysis on the filtered knowledge-base. The dashboard shall include the ability to produce different visualizations of the data based on the filtering and the needed visual outlook. The report documents shall include a detailed outlook on the company finical state as well as projected revenue gains and loss compared to the competitors.
\subsubsection{Action Items}
\begin{itemize}
    \item The development of dashboard that highlights important information and that it differs from dashboard used for Finance
    \item Determination of the best cloud solution for the company
    \item development of the filtering capability
    \item development of the different visualizations for the filtered according to the exploratory analysis
\end{itemize}

\subsection{The second Interview (Admin)}
\subsubsection{Interviewee}
\textbf{Admin}
\subsubsection{Interviewer}
\textbf{Shahd Ahmed}
\subsubsection{Purpose Of The Interview}
The purpose of it is to identify the possible management issues that the admin might face during the supervision of the system,express his opinions about the inclusion of the data management subsystem, and his concerns about analysis done.
\subsubsection{Summary}
The main concerns of the admin are the performance of the exploratory analysis that is going to be done by the system, as well as the management of the data and the ease of modification. The data shall go through a preprocessing stage (i.e. turned in information). There should be a review capability of the reports to make it more comprehensible.
\subsubsection{Action Items}
\begin{itemize}
    \item Assessment of the exploratory analysis performance and possible improvements
    \item Being provided the data that is going to be used in the system.
    \item Preprocessing of data subsystem that is supervised by the admin.
    \item Modifications of data management subsystem to enable easier editing of the data
\end{itemize}

\subsection{The Third Interview}
\subsubsection{Interviewee}
\textbf{Head of finical department}
\subsubsection{Interviewer}
\textbf{Shahd Ahmed}
\subsubsection{Purpose of The Interview}
The purpose is to clarify the information that is going to be included in the finical report of the system as well as identify the rate at which the report is going to be produced.
\subsubsection{Summary}
After asking the main questions, we have found that including a projection of Net profit and Debt Asset ratio is going to be more beneficial, as well as identifying that the following performance metrics should be included(current state and not predictions): Gross profit Margin, Net Profit Margin,Quick Ratio, Current Ratio, Working capital, and Debt-to-equity ratio. The finical reports should be produced monthly, moreover developing an internal currency conversions.
\subsubsection{Action Items}
\begin{itemize}
    \item Inclusion of predictions of net profit and debt asset ratio.
    \item Inclusion of more detailed performance metrics in the reports.
    \item making the interface easier to use to able to sift through the data.
    \item adding capability to display different currencies as well as automatic conversions.
    \item The system shall produce the reports monthly.
\end{itemize}
\section{Interviewer Data}
\begin{table}[h]
    \centering
    \begin{tabular}{l r}
        \toprule
        \textbf{Name}         & Shahd Ahmed                    \\
        \textbf{Title}        & System Analyst                 \\
        \textbf{Phone Number} & +201066642229                  \\
        \textbf{Email}        & \texttt{shahdtaher7@gmail.com} \\
        \bottomrule
    \end{tabular}
\end{table}

\end{document}